Statistical Modeling of Galaxy Catalogues with Normalizing Flows

### 2023-04-12 src/tex/ms.tex
Ack Martine

\author{Alex~I.~Malz}
\affiliation{\note{Alex's affiliation}}

@@

Astronomical data represent realizations of complex probability distributions.
A common goal in research is to infer the underlying distribution from a limited set of noisy data, and use this distribution to estimate posterior distributions over galaxy and population parameters.
An important example is photometric redshift (photo-z) estimation, where galaxy redshift posteriors are estimated from galaxy photometry, using a model informed by a training set of spectroscopic galaxy data \citep{newman2022}.
These redshift posteriors are then used to estimate posterior distributions for cosmological parameters \citep{descSRD}.

@@

\begin{acknowledgements}
    Thanks to François~Lanusse for some early advice on normalizing flows and for reviewing the paper.
    J.~F.~Crenshaw, B.~J.~Kalmbach, and A.~J.~Connolly acknowledge support from the DiRAC Institute in the Department of Astronomy at the University of Washington.
    The DIRAC Institute is supported through generous gifts from the Charles and Lisa Simonyi Fund for Arts and Sciences, and the Washington Research Foundation.
    Z.~Yan acknowledges support from the Max Planck Society and the Alexander von Humboldt Foundation in the framework of the Max Planck-Humboldt Research Award endowed by the German Federal Ministry of Education and Research.

>>>>

\author[0000-0002-8676-1622]{Alex~I.~Malz}
\affiliation{McWilliams Center for Cosmology, Department of Physics, Carnegie Mellon University}

@@

Testing some new text here.

We deleted a sentence here.
A common goal in research is to infer the underlying distribution from a limited set of noisy data, and use this distribution to estimate posterior distributions over galaxy and population parameters.
An important example AND ARE ADDING some new text HERE in the middle of this sentence is photometric redshift (photo-z) estimation, where galaxy redshift posteriors are estimated from galaxy photometry, using a model informed by a training set of spectroscopic galaxy data \citep{newman2022}.
These redshift posteriors are then used to estimate posterior distributions for cosmological parameters \citep{descSRD}.

@@

\begin{acknowledgements}
    Thanks to François~Lanusse for some early advice on normalizing flows and for reviewing the paper, and to Martine Lokken for testing PZFlow.
    J.~F.~Crenshaw, B.~J.~Kalmbach, and A.~J.~Connolly acknowledge support from the DiRAC Institute in the Department of Astronomy at the University of Washington.
    The DIRAC Institute is supported through generous gifts from the Charles and Lisa Simonyi Fund for Arts and Sciences, and the Washington Research Foundation.
    Z.~Yan acknowledges support from the Max Planck Society and the Alexander von Humboldt Foundation in the framework of the Max Planck-Humboldt Research Award endowed by the German Federal Ministry of Education and Research.
    AIM acknowledges support during the course of this work from the Max Planck Society and the Alexander von Humboldt Foundation in the framework of the Max Planck-Humboldt Research Award endowed by the Federal Ministry of Education and Research.
